\begin{problem}{Business Center}{business.in}{business.out}{2 seconds}

% Author: Georgiy Korneev, Text: Roman Elizarov

International Cyber Police Corporation (ICPC) had built a new mega-tall business center
to host its headquarters and to lease some space for extra profit. 
It has so many floors, that it is impractical to have a separate button
in each of its $m$ elevator cars for each individual floor. Instead, each elevator car has just
two buttons. One button in $i$-th elevator car makes it move up $u_i$ floors, 
the other makes it move down $d_i$ floors. The business center is so high, that 
we can ignore its height for this problem (you will never reach the top floor), 
but you cannot go below the ground floor. All floors are numbered by integer 
numbers starting from zero, zero being the ground floor.

You start on the ground floor of the business center. You have to choose one
elevator car out of $m$ to ride on. You cannot switch elevators cars after that.
What is the lowest floor above the ground floor you can get to after you press 
elevator car buttons exactly $n$ times? 

\InputFile

The first line of the input file contains two integer numbers $n$ and $m$
($1 \le n \le 1\,000\,000$, $1 \le m \le 2\,000$)~--- the number of button presses
and the number of elevator cars to choose from. The following $m$ lines
describe elevator cars. Each line contains two integer numbers $u_i$ and
$d_i$ ($1 \le u_i$, $d_i \le 1\,000$).

\OutputFile

Write to the output file a single positive integer number --- the number of the lowest
floor above ground floor that can be reached by one of $m$ elevators after pressing
its buttons exactly $n$ times.

\Example

\begin{example}
\exmp{
10 3
15 12
15 4
7 12
}{
13
}%
\end{example}

\end{problem}
