\begin{problem}{Funny Language}{funny.in}{funny.out}{2 seconds}

% Author: Georgiy Korneev, Text: Roman Elizarov

There is a well know game with words. Given a word you have to write as many
other words as possible using the letters from the given word. If the letter
repeats multiple times in the original word, you can use it up to as many times
in the new words. The order of letters in the original word does not matter.
For example, given the word CONTEST you can write NOTE, NET, ON, TEST, SET, etc.

Now you are in charge of writing a new dictionary. Your task is to sneak $n$
new words into it. You know in advance $m$ words $W_i$ ($1 \le i \le m$)
that you will have to play a game with and you need to figure out which new $n$ words
to add to the dictionary to maximize the total number of words you can
write out of these $m$ words.

More formally, find such a set of nonempty words $S$ where $|S| = n$,
$W_i \notin S$ for any $i$, and $\sum_{1 \le i \le m} |S_i|$ is maximal, where
$S_i \subset S$ is the set of words that can be written using
letters from $W_i$.

\InputFile

The first line of the input file contains two integer numbers $n$
($1 \le n \le 100$) --- the number of new words you can add to the
dictionary and $m$ ($1 \le m \le 1\,000$) --- the number of words you will
play the game with. The following $m$ lines contain original words.
Each word consists of at most 100 uppercase letters from A to Z.

\OutputFile

Write to the output file $n$ lines with a new word on a line.

\Example

\begin{example}
\exmp{
3 5
A
ACM
ICPC
CONTEST
NEERC
}{
C
CN
E
}%
\end{example}

\end{problem}
